Accessing biological data with semantic web technologies

### 2013-12-30 article.tex
Place the examples inside the larger sections for which they are an example
Added an abstract

\newpage
\begin{abstract}
\end{abstract}

@@

\subsection{Example}

>>>>

\newpage
\begin{abstract}
\noindent
\textbf{Background}. Semantic Web technologies are increasingly used in biological database systems.
The improved expressiveness show advantages in tracking provenance and allowing knowledge to be
more explicitly annotated. The list of semantic web standards needs a complementary set of tools to
handle data in those formats to use them in bioinformatics workflows. \\
\textbf{Methods}. The approach proposed in this paper uses the Apache Jena library to create an
environment where semantic web technologies can be use in the statistical environment R. The
code is exposed as two R packages available from the Comprehensive R Archive Network (CRAN). 
The RJava libary and a custom convenience class is used to bridge between R and the Jena library.\\
\textbf{Results}. We here present two examples showing how the Resource Description Framework
(RDF) and SPARQL query standards can be employed in R. The first example takes input on BRCA1 SNPs
from a BioMart and converts this into a RDF data set. The second example runs a query on an
experimental remote SPARQL end point provided by Uniprot, and searches textual annotations of
proteins encoded by the BRCA1 gene. \\
\textbf{Discussion}. The two provided library bring basic semantic web technologies to R.
While only a subset of Apache Jena is currently exposed, it provides key methods to deal with
RDF data and resources. The libraries are freely available from the CRAN under the 
Affero GNU Public Licence version 3: \url{http://cran.r-project.org/web/packages/rrdf/}.
\end{abstract}

@@

\subsubsection{Example}
